\fontfamily{phv}\selectfont{Causal Discovery methods for Effective Connectivity in Human Brains}

### 2014-01-15 docs/paper/paper final.tex
Wrote some more paragraphs for the discussion.

\section{Discussion}
%Good consistency of structure within and between subjects
%cause of poor consistency: inherent to our method or viable for further research?
%data aquisition and noise, improvement in data -> improvement in causal inference
%better methods for direction (Tom's new algorithm), and why that might solve causal inference problems
%run-time is quick
%HRF

@@

% Comparison standard PC and EMS-PC
Both standard PC and EMS-PC find many bi-directional arrows, with some one-directional arrows.

@@

A Bayesian network cannot contain cycles, as that would imply that a variable is it's own ancestor and thus it's own cause.
However, exclusion of cycles in brain networks has not been proven and also seems unlikely.
We believe an interesting direction of further research would thus be to apply cyclical causal discovery.
% TODO: Add citation to Joris Mooij.

% TODO: What do you mean with 'it can also do this'? What does 'this' refer to?
% Computational advantage
%It can also do this quite efficiently, as a few hundred iterations can be run in a matter of hours per subject.
%We have not performed a statistical analysis on the number of iterations needed to stabilise the results.
%It may be possible that a significant result can already be found with much less iterations.

% TODO: Suggereren task based analysis ipv resting state voor beter causaal beeld. 
% TODO: Maak duidelijk welke aannames gedaan worden in welke PC variant en welke aannames verzwakt zouden kunnen worden.

>>>>

\section{Discussion}
%Good consistency of structure within and between subjects

%HRF

% TODO: Maak duidelijk welke aannames gedaan worden in welke PC variant en welke aannames verzwakt zouden kunnen worden.

% Quick run-time
For PC as well as standard PC we were able to run hundreds of iterations on 116 variables in a matter of hours per subject.
Iterations can also be run in parallel.
Further speed increments can be achieved by coding the algorithm in a low overhead language.

@@

% Comparison Markov class standard PC and EMS-PC
Both standard PC and EMS-PC find many bi-directional arrows, with some one-directional arrows.
% TODO: find out how large these groups are.

@@

A causal network or Bayesian network cannot contain cycles by definition.
However, exclusion of cycles in brain networks has not been proven and also seems unlikely.
We believe an interesting direction of further research would be to apply cyclical causal methods, such as the method proposed by Mooij and Heskes\cite{Mooij20013}.

We believe application of a Bayesian approach will provide a better insight.
Standard PC and EMS-PC lack a robust measure of uncertainty.
There is no baseline or correctness measure to compare results or data with
A Bayesian approach such as proposed by Claassen and Heskes will provide more slack and insight in results \cite{claassen2012}.
This in turn might leverage development of better and faster data driven methods.

% TODO: Suggereren task based analysis ipv resting state voor beter causaal beeld.

%cause of poor consistency: inherent to our method or viable for further research?
